A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-26 rr-flow.Rmd
add summary

```
FROM rocker/verse:3.6.1
RUN install2.r --error --skipinstalled\
  pacman here pander
WORKDIR /home/rstudio
```

@@

! TODO - Summary of all this and all benefits

@@

How to best share a reproducible workflow? We believe that, ideally, a service provider should be found that guarantuees permanent and reliable hosting of the reproducible workflow, such as the Open Science Framework (citation needed) or PsychData (citation needed). Second, to ensure that other users are legally able to benefit from the shared materials, authors must choose an appropriate license format. Typically, there is currently no single license that works for code, data, and media (such as text or figures). We encourage authors to choose appropriate license forms that do not hinder others from freely downloading, using, and moifying the shared workflows and materials while, at the same time, ensuring recognition for the time and effort invested in creating the workflow in the first place. In our experience, the Creative Commons license (CC-BY) is often appropriate for sharing texts, rmarkdown files, generated figures, and other media whereas scripts and any other computer code is often best shared according to the MIT license. Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work. These licenses are also in line with the recommendations by the Reproducibile Research Standard (see @stoddenEnhancingReproducibilityComputational2016).

>>>>

```
FROM rocker/verse:3.6.1
RUN install2.r --error --skipinstalled\
  pacman here pander
RUN installGithub.r\
  crsh/papaja benmarwick/wordcountaddin
WORKDIR /home/rstudio
```

@@

The overarching goal of this paper was to provide an easy to use workflow, that allows confidence in reproducibility. This workflow can be almost unfailingly trusted to be replicable with the following commands:

```{bash, eval=FALSE}
git clone https://github.com/aaronpeikert/reproducible-research.git
cd reproducible-research
make build
make all DOCKER=TRUE
```

That is, it replicates a scientific report exactly without regard to the user, the operating system, the software, the timepoint or the version of the files. To that end, it relies on tools that have been the foundation of reliable software for years or in most cases, decades. On the way, it makes transparent how statistical results relate to the software that created them and enables, through that transparency, reuse by other researchers.

Each tool reduces the number of ways things can go wrong. Dynamic reporting with `RMarkdown` fixes the relation between statistical report and statistical results; Version control with `git` fixes the version of the used files; Dependency management with `make` fixes relation of files and their processing; Containerization with `docker` fixes the software environment. This tightening of loose ends, we believe, does not restrict the researcher but enables her to operate on a solid basis to deliver sound research.

@@

How to best share a reproducible workflow? We believe that, ideally, a service provider should be found that guarantuees permanent and reliable hosting of the reproducible workflow, such as the Open Science Framework [@fosterOpenScienceFramework2017] or PsychData (citation needed). Second, to ensure that other users are legally able to benefit from the shared materials, authors must choose an appropriate license format. Typically, there is currently no single license that works for code, data, and media (such as text or figures). We encourage authors to choose appropriate license forms that do not hinder others from freely downloading, using, and moifying the shared workflows and materials while, at the same time, ensuring recognition for the time and effort invested in creating the workflow in the first place. In our experience, the Creative Commons license (CC-BY) is often appropriate for sharing texts, rmarkdown files, generated figures, and other media whereas scripts and any other computer code is often best shared according to the MIT license. Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work. These licenses are also in line with the recommendations by the Reproducibile Research Standard (see @stoddenEnhancingReproducibilityComputational2016).
